---
title: "exploration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{exploration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(RefPesticidesBzh)
```

<!--

# Description du package

Ce package permet d'actualiser et d'exploiter un référentiel des substances actives pesticides à partir des informations obtenues à partir de plusieurs référentiels nationaux, notamment AGRITOX, EPHY. Il inclut les corrections et compléments apportés par le groupe de travail régional animé par l'Observatoire de l'Environnement en Bretagne.
--> 


# Read data

<!-- Store your dataset in a directory named "inst/" at the root of your project -->
<!-- Use it for your tests in this Rmd thanks to `load_all()` to make it available
and `system.file()` to read it in your examples 
-->


# Télécharger un jeu de données référentiel

```{r examples}
import_dataset('https://www.data.gouv.fr/fr/datasets/r/98dbe26f-a2e4-4002-a598-c226bf6af664','agritox','zip')
```

# Lire les métadonnées du jeu de données à partir de la page data.gouv.fr

## Use sub-functions in the same chunk

```{r examples-1}
metadonnees_dataset('https://www.data.gouv.fr/fr/datasets/base-de-donnees-agritox/')
```

# There can be development actions

These will be included in the `dev_history.R` file of your package, but won't be direct part of it.


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory

